---
title: "Project"
author: "Mechaque Alex Muiuane"
date: "April 18, 2017"
output: html_document
---
===============================================================================

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## here I will load the necessary data for this project.

he variables included in this dataset are:

steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
date: The date on which the measurement was taken in YYYY-MM-DD format
interval: Identifier for the 5-minute interval in which measurement was taken
The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset
```{r}
getwd()
 setwd("E:/DScience/Reproducible_Research/Week2/Project-Assignment")
dir()

activityData <- read.table("./activity.csv", sep = ",",header = TRUE)
activityData <- activityData[with (activityData, { !(is.na(steps))}),]

head(activityData)
```
## Histogram of the total number of steps taken each day

Code bellow will produce an histgram of the total number of steps taken each day.

```{r}
totalsInDay <- activityData  
  filter(!is.na(steps)) 
  group_by(date) 
  summarise(steps =sum(steps, na.rm = TRUE))
hist(totalsInDay$steps, breaks = 25, col = "blue", main = "Total steps", xlab = "total steps")
```

  ## this pare of the assignment will for calculatin the mean and median of number of steps taken each day
```{r}
sumBySteps <- group_by(activityData, date)
head(sumBySteps)

meanMed <- summarize(sumBySteps, total = sum(steps))
summary(meanMed)
```
## This is the plot of time series 
```{r}
meanMed_per_day <- aggregate(steps ~ interval, activityData, mean)
plot(meanMed_per_day$interval, meanMed_per_day$steps, type = "l", main = "average number", xlab = "interval", ylab = "average" )
```
## The 5-minute interval that, on average, contains the maximum number of steps
```{r}
subset_Max_steps <- which.max(meanMed_per_day$steps)
meanMed_per_day[subset_Max_steps, ]
```
# Code to describe and show a strategy for imputing missing data
## for the perpouse of this question, I added a new dataset containing all the information of the original data.
```{r}
activityDataSource <- read.table("./activity.csv", sep = ",",header = TRUE)
head(activityDataSource)
sum(is.na(activityDataSource))
mean(is.na(activityDataSource))
activityDataclean <- activityData[with (activityData, { !(is.na(steps))}),]
```
# Histogram of the total number of steps taken each day after missing values are imputed
```{r}
hist(activityDataclean$steps, main = "Histogram # steps cleaned", xlab = "Total")
```




